\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex

\section{Reviewer 2's Comments}

\textit{This paper covers the fabrication and integration of a new soft robot gripper with a six degree of freedom soft multi-segment arm. The paper also describes a planner for grasping using the integrated system as well as some evaluation of grasping efficacy and the gripper workspace.}

\textit{In general, I think the topic is very interesting and the approach valuable. There seems to be a number of practical limitations to the platform and approach that I would like to see addressed or discussed in the paper. The following are specific feedback that I have:}

\subsection{Uncertainty Characterization}
\textit{For the third contribution listed on page 2 (line 33), I don't agree that you have characterized some of the uncertainty that is rather important. For example, you have shown for the gripper where it can grab for a single set of trials, but you do not describe repeating those trials, which would actually give you measures of uncertainty. Also, the red box used to denote the "bin" for placing the grasped object is an important measure of uncertainty. It seems like if this arm were to actually be used for manipulation, a good measure of uncertainty on positional accuracy would be important.}
Thank you for this comment. The capture region characterization was performed three times, always yielding to the same capture region given the grid size. The intent of this experiment was to qualitatively describe a relation between object size to gripper size to area of successful grasp. 
We revised the manuscript to properly phrase the contribution and provide the missing details on the experimentation.
\subsection{Delicate Object Manipulation}
\textit{For the fourth contribution listed on page 2 (about line 37), I don't believe that you have shown (either experimentally or analytically) that you can manipulate delicate objects. I believe it, but you haven't reported gripper forces or extensive trials with delicate objects. I would either perform those tests or rewrite this contribution. It also isn't clear what is meant by "proper manipulation."}
Thank you for this observation, we added the missing details to the paper. We rewrote the Grasping delicate objects section to provide more detail on what delicate objects have been successfully grasped, pointing out that the egg is just one example. We also describe how blocking force and pressures have been analyzed for the gripper and how the small range .
\subsection{Clearer Fabrication Process Description}
\textit{I found the description of the fabrication process for the gripper to be slightly confusing. I think more annotations on figure 3 (such as point 1 or c, etc) and referring to those annotations in the description could make it clearer. Especially since this is listed as a major contribution.}
Figure 3’s point 1 and c were modified according to your suggestion and more descriptive note were added to the fabricationg figure and the description in the paper.
\subsection{Distinguishing from Past Work}
\textit{Although you reference past papers from your own group, I think you could do a better job distinguishing from your own past work. Can the process for making the gripper be applied to the multi-segments as well? Which is better for what and why?}
We revised the exposition to clarify this point. We added to the Lost Wax Fabrication section theses sentences:
"The retractable pin fabrication for uniform lateral channels, first introduced in reference [12], does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes. This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper."
Later in the multi-segment arm section, we also added:
"The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities."
\subsection{Limitations that could be Addressed}
\textit{Many limitations of the hardware or approach should be addressed in the paper. I realize that they cannot all be addressed or discussed. Nor am I asking for you to solve these problems, but an effort could be made to talk about the following:}
See our answers below.
\item \textit{How would the design of the gripper change if we wanted to grip in both directions? Is it even possible with the current design?}
We added to the limitations discussion in the manuscript:
"The experiments were only performed for picking up objects on the left quadrant of the manipulator. Grasping objects in both directions could be achieved in various ways by 
\item increasing the reachable workspace through starting the soft arm at an extreme curvature configuration within the right quadrant,
\item replacing the large gripper with two smaller grippers next to each other at the end of the arm, 
\item mounting roller supports on the top face of the manipulator and then rotating the manipulator at its root by $180^{\circ}$."  

@@

\end{enumerate}
%
\item \textit{Is using motion tracking realistic for some of the scenarios you suggest? I would guess not, but what is the future for state estimation? Existing sensors? Or are new sensors needed?}
We added:
"It is worth mentioning that the exteroceptive tracking system has the disadvantage that a full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. In that case, the control loop can not function properly until the occlusion disappears. Proprioceptive sensors within the segments can solve this issue. A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9]."

@@

"It is worth mentioning that the exteroceptive tracking system has the disadvantage that a full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. In that case, the control loop can not function properly until the occlusion disappears. Proprioceptive sensors within the segments can solve this issue. A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9]."
%
\item \textit{It requires 6 degrees of freedom to achieve a reasonable reachable work space, how does this scale to a full 6 DoF task? Or does it scale? Is it limited to in-plane tasks? What is the reachable work space in the plane with 6 DoF and the + or - 60 degree joint limit?}
Thank you for this observation. The focus of the paper is planar manipulation. Scaling to a 3-dimensional task is not considered in this paper. Our current work will consider the 3D case.
We revised the text to clarify this point, we added in the multi-segment arm section: 
"As was shown in [13] through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robot arm that can create high blocking forces per fluid energy inserted."
We also added to the same section:
"Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base. Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl." 

@@

"Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base. Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl." 
%
\item \textit{Why was a convex shape necessary for approaching a grasp? What if I wanted to approach an object with a different orientation but in the same locations you already looked at?}
We added an emphasis to the manuscript to say that the shape needs not be convex. The convex shape approach is a conservative solution with minimal computation required in solving the planning problem while assuring not to collide. 

@@

We added an emphasis to the manuscript to say that the shape needs not be convex. The convex shape approach is a conservative solution with minimal computation required in solving the planning problem while assuring not to collide. 
%
\item \textit{What is the role of the rollers in carrying your payload? Without the rollers, could the arm not move the object?}
Thank you for this comment, we added to the multi segment arm section:
"The complete multi-segment arm is supported off the ground with two roller supports per segment. 
The rollers minimize frictional forces to the surface. 
If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful."

@@

If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful."
%
\item \textit{Why did you decide to minimize manipulator deformation for your grasp object planner? Furthermore, what if I wanted my plan to follow the shortest distance for the end effector to travel (essentially following the black line in Figure 6), is this even possible given the possible kinematics of the arm?}
Minimized manipulator deformation seemed to be a feasible approach, because it is proportional to energy consumed by the cylindrical piston drives and it minimizes strain to the actuators and minimizes risk of exerting further than actuation limit of a segment. We also added this explanation to the paper. 

### 2015-10-11 experimental_results.tex
finished reviewer 2's comments

\subsection{Experimental Insights and Limitations}
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
Most of the payload capability is already used up by the attached gripper itself.
A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper. A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that an occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. In that case, the control loop can not function properly until the occlusion disappears. Proprioceptive sensors within the segments can solve this issue.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E. Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red. Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively. }
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

>>>>

\subsection{Experimental Insights and Limitations}
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
Most of the payload capability is already used up by the attached gripper itself.
A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper. A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. In that case, the control loop can not function properly until the occlusion disappears. Proprioceptive sensors within the segments can solve this issue. A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E. Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red. Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

\rkk{The experiments were performed for picking up objects on the left quadrant of the manipulator.
Grasping objects on both sides of the manipulator could be achieved in various ways by 
\begin{enumerate}
\item replacing the large gripper at the end of the arm with two smaller grippers next to each other, 
\item mounting roller supports on the top face of the manipulator and then rotating the manipulator at its root by $180^{\circ}$,
\item increasing the reachable workspace through starting the soft arm at an extreme curvature configuration within the right quadrant.  
\end{enumerate}
}

### 2015-10-11 processing_control.tex
finished reviewer 2's comments

\subsection{Autonomous Grasp-and-Place System}
\label{subsec:grasp-place-planner}
The robotic manipulation system is capable of autonomously performing grasp-and-place operations. 
A state flow diagram describing its sensing, planning and executions states is given in Fig. \ref{fig:grasp-and-place-planner}. 
A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle.
\rkk{We consider the object to have settled if it has not moved by more than a small $\epsilon$ for 2\unit{s}}.
After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there. 
Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, bending away from the object. 
Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
This planner is described in more detail in Section~\ref{subsec:grasp_planner}.

@@

The Grasp Object Planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses these to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
During the arm initialization, the new curvature controller performs a pre-pressurization of both lateral channels. 
This is only done for the two segments closest to the root of the arm in order to stiffen them and shorten their response time constant.  
To allow for smoother transitions between each configuration $\boldsymbol{\kappa}_i^*$, we also added a trajectory generation procedure \texttt{trajGen()} to the new curvature controller. It generates in real-time for each individual degree-of-freedom velocity profiles with acceleration and velocity constraints.
These profiles allow real-time interpolation between the approach configurations of the arm and avoid overshooting at the next target configuration.
When the arm has arrived at the object, the curvature controller initiates \texttt{graspObject()}.
After encapsulating the object, \texttt{moveToBin()} requests \texttt{trajGen()} for another trajectory from the current pose to a pre-defined bin location.
After the manipulator has arrived at the bin location, the procedure \texttt{releaseObject()} causes the gripper to open and release the object.

@@

We refer to these as approach configurations.
The process for determining these approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
The planner is visualized in Figure \ref{fig:planGrasp}.
In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1.. numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these \rkk{green} circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.

@@

The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
This process is posed as a nonlinear optimization. 
Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle. 
This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm \ref{alg:planGrasp} for convenience.

>>>>

\subsection{Autonomous Grasp-and-Place System}
\label{subsec:grasp-place-planner}
The robotic manipulation system is capable of autonomously performing grasp-and-place operations. 
A state flow diagram describing its sensing, planning and executions states is given in Fig. \ref{fig:grasp-and-place-planner}. 
A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle.
\rkk{We consider the object to have settled if it has not moved by more than a small $\epsilon$ for 2\unit{s}}.
After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there. 
Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, \rkk{always} bending away from the object. 
\rkk{This is a conservative approach requiring minimal computation to solve the planning problem of not prematurely colliding with the object.} 
Furthermore, \rkk{this approach} allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
This planner is described in more detail in Section~\ref{subsec:grasp_planner}.

@@

The Grasp Object Planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses these to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
During the arm initialization, the new curvature controller performs a pre-pressurization of both lateral channels. 
This is only done for the two segments closest to the root of the arm in order to stiffen them and shorten their response time constant.  
To allow for smoother transitions between each configuration $\boldsymbol{\kappa}_i^*$, we also added a trajectory generation procedure \texttt{trajGen()} to the new curvature controller. It generates in real-time for each individual degree-of-freedom velocity profiles with acceleration and velocity constraints.
These profiles allow real-time interpolation between the approach configurations of the arm and avoid overshooting at the next target configuration.
When the arm has arrived at the object, the curvature controller initiates \texttt{graspObject()}.
After encapsulating the object, \texttt{moveToBin()} requests \texttt{trajGen()} for another trajectory from the current pose to a pre-defined bin location.
\rkk{When the manipulator gets close to the bin location}, the procedure \texttt{releaseObject()} causes the gripper to open and release the object.

@@

We refer to these as approach configurations.
The process for determining these approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
The planner is visualized in Figure \ref{fig:planGrasp}.
In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1.. numMoves$ that define concentric \rkk{green} circles shrinking from the manipulator's starting tip pose towards the center of the object.
Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these \rkk{green} circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.
\rkk{Minimized manipulator deformation is chosen as the optimization criterion, because it is proportional to the energy consumed by the fluidic drive cylinders and it also minimizes the strain to the soft actuators.}

@@

The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
This process is posed as a nonlinear optimization. 
Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle. 
This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm~\ref{alg:planGrasp} for convenience.

### 2015-10-11 robotic_gripper.tex
finished reviewer 2's comments

The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
 \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
Each cylindrical segment can only be actuated up to a bend angle of less than $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane. 
The cylindrical design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip. 
The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.

>>>>

The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
\rkk{As was shown in \ref{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
 \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
Each cylindrical segment can only be actuated up to a bend angle of about $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane. 
\rkk{Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base. Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip. 
The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.

\rkk{The complete multi-segment arm is supported off the ground with two roller supports per segment. 
The rollers minimize frictional forces to the surface. 
If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful.}
